---
output:
  pdf_document: default
  html_document: default
---
**The dataset consists the profit statement for 50 companies and various additional**    
**variables associated with those companies. This script is meant to develop a model**    
**where we can predict as to which particular variable(s) contribute most towards**    
**the profit of those companies and which company is most profitable**    

**1. Import the dataset**    
```{r}
dataset = read.csv('50_Startups.csv')
```    

**2. Encode categorical data**    
```{r}
dataset$State = factor(dataset$State,
                       levels = c('New York', 'California', 'Florida'),
                       labels = c(1, 2, 3))
```    

**3. Split the dataset into training and test set**    
```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$Profit, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```    

**4. Fitting Multiple Linear Regression to the Training set**    
```{r}
regressor = lm(formula = Profit ~ .,
               data = training_set)
```    

**5. Predict the test set results**    
```{r}
y_pred = predict(regressor, newdata = test_set)
y_pred
test_set
```    

**6. Result**    

**As one can see, y_pred represents the model's predicted profiit values for the**    
**test set. The values are close to the test set.**    
