---
output:
  pdf_document: default
  html_document: default
---
**this script is meant to verify the salary of a potential employee in his/ her**    **previous company. We will use support vector regression model to learn from the**     **position salary dataset of the potential employee's previous company and predict**     **whether the potential employee earned 160k salary as a regional manager**    

**1. Import the dataset**    
```{r}
dataset = read.csv('Position_Salaries.csv')
dataset = dataset[2:3]
```

**2. Fit Polynomial Linear Regression to the dataset**    
```{r}
dataset$Level2 = dataset$Level^2
dataset$Level3 = dataset$Level^3
dataset$Level4 = dataset$Level^4
poly_reg = lm(formula = Salary ~ .,
              data = dataset)
```    

**3. Visualize**    
```{r}
library(ggplot2)

x_grid = seq(min(dataset$Level), max(dataset$Level), 0.1)

ggplot() + 
        geom_point(aes(x = dataset$Level, y = dataset$Salary), colour = 'red') + 
        geom_line(aes(x = x_grid, 
                      y = predict(poly_reg,
                                        newdata = data.frame(Level = x_grid,
                                                             Level2 = x_grid^2,
                                                             Level3 = x_grid^3,
                                                             Level4 = x_grid^4))),
                  colour = 'blue') + 
        ggtitle('Truth or Bluff (Polynomial Regression)') + 
        xlab('Level') + ylab('Salary')
```    

**4. Predict the result**    
```{r}
predict(poly_reg, data.frame(Level = 6.5,
                             Level2 = 6.5^2,
                             Level3 = 6.5^3,
                             Level4 = 6.5^4))
```    

**5. Result**    

**As one can see, this model predict the salary for the position to be 158k, whereas the actual salary is 160k**    


