---
output:
  pdf_document: default
  html_document: default
---
**this script is meant to verify the salary of a potential employee in his/ her**    
**previous company. We will use support vector regression model to learn from the**    
**position salary dataset of the potential employee's previous company and predict**    
**whether the potential employee earned 150k salary as a regional manager**    

**1. Importing the dataset**    
```{r}
dataset = read.csv('Position_Salaries.csv')
dataset = dataset[2:3]
```    

**2. Fitting Random Forest Regression to the dataset**    
```{r}
library(randomForest)
set.seed(1234)
regressor = randomForest(x = dataset[-2],
                         y = dataset$Salary,
                         ntree = 500)
```    

**3. Predicting a new result with Random Forest Regression**    
```{r}
y_pred = predict(regressor, data.frame(Level = 6.5))
y_pred
```    

**4. Visualising**    
```{r}
library(ggplot2)

x_grid = seq(min(dataset$Level), max(dataset$Level), 0.01)

ggplot() + 
        geom_point(aes(x = dataset$Level, y = dataset$Salary), colour = 'red') +
        geom_line(aes(x = x_grid, y = predict(regressor, newdata = data.frame(Level = x_grid))),
                  colour = 'blue') +
        ggtitle('Truth or Bluff (Random Forest Regression)') +
        xlab('Level') + ylab('Salary')
```    

