---
output:
  pdf_document: default
  html_document: default
---
**This script is meant to use Linear Regression model**

**The dataset consists of 30 rows and 2 columns; where each row comprises of an** **employee and the 2 columns comprise of Years of Experience and Salary of each** **employee. The goal of this script is too use a Simple Linear Regression model**
**to check and see if the independent variable (Years of Experience) for each**
**employee can be used to predict the dependent variable (Salary)** 

**1. Set working directory, import the libraries and the dataset**
```{r}
dataset = read.csv("Salary_data.csv")
```     

**2. Split the dataset into  training and test set**         
**load caTools library**    
```{r}
library(caTools)
```     
**3. set seed**    
```{r}
set.seed(123)
```     

**4. split the dependent variable where 2/3 goes to training set and rest to test**
```{r}
split = sample.split(dataset$Salary, SplitRatio = 2/3)
```    

**5. use the split to make training and test sets**    
```{r}
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```    

**6. Fitting Simple Linear Regression to the Training set**
```{r}
regressor = lm(formula = Salary ~ YearsExperience,data = training_set)

```     
**View the regressor**
```{r}
summary(regressor)
```    
**Predicting the Test set results**    
```{r}
y_pred = predict(regressor, newdata = test_set)
```    
**7. Visualize the training set results**    
```{r}
library(ggplot2)
ggplot() +
        geom_point(aes(x = training_set$YearsExperience,
                       y = training_set$Salary),
                   colour = 'red') +
        geom_line(aes(x = training_set$YearsExperience,
                      y = predict(regressor, newdata = training_set)),
                  colour = 'blue') +
        ggtitle('Salary vs Experience (Training Set)') +
        xlab('Years of Experience') +
        ylab('Salary')
```    
**8. Visualize the test set results**    
```{r}
library(ggplot2)
ggplot() +
        geom_point(aes(x = test_set$YearsExperience,
                       y = test_set$Salary),
                   colour = 'red') +
        geom_line(aes(x = training_set$YearsExperience,
                      y = predict(regressor, newdata = training_set)),
                  colour = 'blue') +
        ggtitle('Salary vs Experience (Test Set)') +
        xlab('Years of Experience') +
        ylab('Salary')
```        
        
```    
