---
output:
  pdf_document: default
  html_document: default
---
**This script is meant to verify the salary of a potential employee in his/ her**
**previous company. We will use support vector regression model to learn from the**
**position salary dataset of the potential employee's previous company and predict**
**whether the potential employee earned 150k salary as a regional manager**    

**# 1. import the libraries, dataset and change the working directory**
```{r}
library(caTools)
library(e1071)

dataset = read.csv('Position_Salaries.csv')
dataset = dataset[2:3]
```    

**2. data pre-processing**

**view the dataset**
```{r}
head(dataset)
```    

**we arent splitting the dataset into training and testing set because we want the**
**model we create to learn from all the data and to find any (if any) correlation**
**between the 'Position' and the 'Salary' we apply the feature scaling in this**
**dataset to the dependent variable ('Salary'); because the values of the dependent**
**variable ('Salary') is way greater than the independent variable ('Position').**
**This can result in the 'Salary' variable affecting the model and hence 'Position'** 
**variable might get neglected**    

**3. Training the SVR model on the entire dataset**    
```{r}
regressor = svm(formula = Salary ~ .,
                data = dataset,
                type = 'eps-regression',
                kernel = 'radial')
```    
**4. predicting a new result**    
```{r}
y_pred = predict(regressor, data.frame(Level = 6.5))
```    

**5. visualizing the SVR results**    
```{r}
library(ggplot2)
ggplot() + 
        geom_point(aes(x = dataset$Level, y = dataset$Salary), colour = 'red') + 
        geom_line(aes(x = dataset$Level, y = predict(regressor, newdata = dataset)), 
                  colour = 'blue') + 
        ggtitle('Support Vector Regression') + 
        xlab('Level') + ylab('Salary')
```    

**6. Result**    
**The position level of 6.5 salary is predicted to be around 170k, which is close**
**to what the employee's salary of 150k was**    